---
title: "Untitled"
output: html_document
---

 first, read 'loan.csv' and save it to dataset
```{r}
dataset <- read.csv("loan.csv")
```

check all the variable if there's any zero variant variable and check for the NA data
```{r}
library(caret)
noVar <- nearZeroVar(dataset)
anyNA(dataset)
```
there's no zero variance variable and no NA data.

we didn't need to split the data into trainset and testset, random forest already have out-of-bag estimates (OOB) that can be used as a reliable estimate of its true accuracy on unseen examples.

now, i'm going to make a fanrom forest model with 4 fold cross validation and 2 repeats
```{r}
set.seed(100)
ctrl <- trainControl(method="repeatedcv", number=4, repeats=2)
forest <- train(default ~ ., data=dataset, method="rf", trControl = ctrl)
```

```{r}
forest
```

the best accuracy we get from mtry 18 with the accuracy of 75.55%

i want to try to build another random forest model with 3 number folds and 2 repeats

```{r}
set.seed(100)
ctrl <- trainControl(method="repeatedcv", number=5, repeats=3)
forest1 <- train(default ~ ., data=dataset, method="rf", trControl = ctrl)
```

```{r}
forest1
```

the first result is still better than the second model, so i will use the forest model. now i will plot the model.
```{r}
plot(forest)
```

as we can see above, mtry 18 get the best accuracy.

```{r}
plot(forest$finalModel)
legend("topright", colnames(forest$finalModel$err.rate),col=1:6,cex=0.8,fill=1:6)
```
```{r}
forest$finalModel
```
it turns out the yes got more than 0.5 error, so i will try to make another model with 1000 trees instead of just 500 trees(default)

```{r}
set.seed(100)
ctrl <- trainControl(method="repeatedcv", number=4, repeats=2)
forest2 <- train(default ~ ., data=dataset, method="rf", trControl = ctrl, ntree = 1000)
```

```{r}
forest2
```

this result is worse than the original model, i will use 'forest' model as the final result.
for this model, recall value is more important than accuracy,
the 'forest' model also have the best recall compare to other models.


```{r}
recall <- 136/(79+136)
prec <- 136/(164+136)
accu <- (621+136)/(621+79+164+136)
paste("Recall:", recall)
paste("Precision:", prec)
paste("Accuracy:", accu)
```










